\documentclass[12pt]{article}

\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage[margin=1in,includefoot]{geometry}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}






\begin{document}

\section*{ \Large Disruptive Innovations }
\raggedright \Large This entails converting high-priced, difficult-to-use, and inaccessible goods and services into simpler and more cheap alternatives.
Disruption is happening all over the healthcare industry, from AI to robotics.

3D printing and robots to health
\\
\section*{Disruptive Healthcare Technology:}
\begin{itemize}
 \item Consumer devices, wearables and apps : Patients could only acquire biometric data when they went to the doctor's office in the past, thanks to consumer devices, wearables, and apps. Consumers can now play a new role in their health journey thanks to data obtained from smartwatches and mobile activity trackers.
 
 \item AI and machine learning :In healthcare, AI applications may be found everywhere, from patient intake to predictive analytics to new drug development. The way health systems work and how care is delivered is changing as a result of this technology.

\item Telemedicine : COVID-19 has hastened the spread of telemedicine, but it has had long-term consequences. In the future, the majority of patients indicate they want to use virtual treatment.

\item Blockchain : Blockchain is a database system that improves data security and usability by storing data in a distributed ledger. Many parts of healthcare are altering as a result of this innovation, including patient records, supply and distribution, and research.

\end{itemize}

\section*{What leads to disruptive innovation?}
\begin{itemize}

\item Complex Experiences : Health sector has the no variety and breadth—such intricate funding methods, the various moving components, the complicated clientele with diverse requirements, and so many possibilities and interventions for any one person’s needs

\item  Confusion : Patients may be perplexed by how medical equipment are used. They may be perplexed about their reports, such as which one is for which purpose.

\item Limited access : In the same way that there is nothing nice about healthcare in rural regions. Even doctors don't have that experience. The lack of availability of equipment and the complicated process of using it leads to equipment innovation or improvement.
\end{itemize}


\section*{Main areas for the application of disruptive innovation in health care: }
\begin{itemize}





\item To support these new models of care, new technologies for early diagnostics, community-based therapy, and care are required.

\item  Treatment of patients with numerous chronic diseases, as well as conditions of frailty and loss of functions, with a person-centered approach;

\end{itemize}




\end{document}